Maintenance planning on French military aircraft operations

### 2018-08-22 R/presentations/CLAIO_presentation/presentation.Rmd
Added files for CLAIO presentation.

---
title: "Maintenance planning on French military aircraft operations"
author: |
    | Franco Peschiera, Alain Haït, Olga Battaïa, Nicolas Dupin
institute: "ISAE SUPAERO"
date: "June 27, 2018"
output: 
  beamer_presentation:
    theme: "Berlin"
    toc: true
    slide_level: 2
    incremental: yes
    fig_height: 4
    # footer: "ISAE-SUPAERO, Université de Toulouse, France"
    includes:
        in_header: header.tex
  slidy_presentation:
    css: ./../../css/baobab_MH.css
    incremental: yes
    footer: "ISAE-SUPAERO, Université de Toulouse, France"
    slide_level: 2
    toc: true
nocite: '@*'
bibliography: MFMP.bib
editor_options: 
  chunk_output_type: console
---

@@

<!-- # Introduction -->

<!-- ## Introduction -->

<!-- Flight and Maintenance Planning (FMP) problems are raised in civilian or military operational applications.  -->

<!-- They schedule maintenances of aircraft taking into account the implications of maintenance immobilizations for the demand in flight hours, for a conjoint optimization among maintenance dates and flight hours. -->

@@

* A series of $j \in \mathcal{J}$ tasks are planned along a horizon divided into $t \in \mathcal{T}$ periods. Since all tasks are already scheduled, we know time periods $T_j \subset \mathcal{T}$ in which they will be realized. 
* Each task requires a certain number $r_{j}$ of resources $i \in \mathcal{I}$ which it employs for a time duration defined by $h_j$ in each period.
* Resources require recurrent preventive maintenance operations since the realization of tasks diminish their remaining usage time.
* A maintenance operation takes exactly $m$ periods and cannot be interrupted. It restores the resource's remaining usage time to exactly $H$ units.

@@

* FMP: Flight and Maintenance Planning problem.
* In @Cho2011, US Army aircraft were assigned daily operations over a year to aircraft in order to minimize the maximum number of maintenances.
* In @Kozanidis2008, Greek aircraft had monthly assignments of maintenances and flight hours in order to maximize the availability and final state of squadrons.
* In @Verhoeff2015, monthly assignments were done and several objectives were taken into account: availability, serviceability and final state.
* In @Chastellux2017, an initial version of the model was done, assigning missions instead of only flight hours.

@@

* The present model deals with an heterogeneous fleet, with different standards and capacities.
* Multiple objectives have been incorporated in order to satisfy the French Air Force's specific needs.
* Asignments to missions are done instead of assignments of flight hours.
* This model also features several improvements in the MIP modelling that permit greater instance sizes.

@@

The following instances were tested:

| id | $\|\mathcal{J}\|$ |$\|\mathcal{T}\|$ |  assign |  objective  |  time (s) |   bound |
|-----|------------------|------------------|---------| ------------| -----------| --------|
| I_0 |                9 |               11 |     310 |        62.0 |        0.7 |    62.0 |
| I_1 |                9 |               21 |     650 |        63.0 |       68.7 |    63.0 |
| I_2 |                9 |               31 |     990 |        63.0 |     3600.1 |    62.0 |
| I_3 |                9 |               41 |    1249 |        64.0 |     3603.9 |    61.7 |
| I_4 |               10 |               11 |     530 |        82.0 |        0.9 |    82.0 |
| I_5 |               10 |               21 |    1070 |        83.0 |      144.0 |    83.0 |
| I_6 |               10 |               31 |    1610 |        83.0 |     3600.1 |    82.0 |
| I_7 |               10 |               41 |    2069 |        84.0 |     3609.1 |    81.8 |
| I_8 |               11 |               11 |    1080 |       139.0 |      530.6 |   139.0 |
| I_9 |               11 |               21 |    2120 |       149.0 |     3600.0 |   139.9 |

@@

The analysis of the solution progress for all instances shows that:

* Initial solutions are quite far from the linear relaxation.
* Branching does not improve significantly the lower bound.

\pause
```{r out.width="150pt", echo=FALSE}
knitr::include_graphics("../img/progress.png.png" %>% paste0(path_to_R_dir, .))
```

*(Progress diagram for instance id=I_7).*

## Multi-objective (1)

Comparison of two objectives: max availability or maintenance capacity.
Different weights were used for the two objectives: $W_1, W_2 \in [0..1]$ with pace of 0.1.
\pause
```{r out.width="180pt", echo=FALSE}
knitr::include_graphics("../img/multiobjective.png" %>% paste0(path_to_R_dir, .))
```

*(Pareto diagram for instance id=I_5).*

## Multi-objective (2)

* Analysis for all instances: not many Pareto optimal points available (between two and four).
* The objectives are quite aligned one with the other.

@@

## Current steps

* **Linent objectives**: minimized total number of maintenances with a hard maximum on total maintenances per month.
* **Multiple solvers**: GUROBI, CPLEX, CBC, CPO, CHOCO.

@@

* **Add useful cuts**: for example limiting maintenance possibilities.
* **Break symmetries**: clustering candidates, fixing end availabilities.
* **Add more constraints**: minimal duration of assignments, storage of aircraft.
* **Add robustness**: duration of maintenances, new /different missions, unavailable aircraft.

>>>>

---
title: "Maintenance planning on French military aircraft operations"
author: |
    | Franco Peschiera, Alain Haït, Olga Battaïa, Nicolas Dupin
institute: "ISAE SUPAERO"
date: "September 24, 2018"
output: 
  beamer_presentation:
    theme: "Berlin"
    toc: true
    slide_level: 2
    incremental: yes
    fig_height: 4
    # footer: "ISAE-SUPAERO, Université de Toulouse, France"
    includes:
        in_header: header.tex
  slidy_presentation:
    css: ./../../css/baobab_MH.css
    incremental: yes
    footer: "ISAE-SUPAERO, Université de Toulouse, France"
    slide_level: 2
    toc: true
nocite: '@*'
bibliography: MFMP_NRP.bib
editor_options: 
  chunk_output_type: console
---

@@

@@

* FMP: Flight and Maintenance Planning problem.
* A series of $j \in \mathcal{J}$ tasks are planned along a horizon divided into $t \in \mathcal{T}$ periods. Since all tasks are already scheduled, we know time periods $T_j \subset \mathcal{T}$ in which they will be realized. 
* Each task requires a certain number $r_{j}$ of resources $i \in \mathcal{I}$ which it employs for a time duration defined by $h_j$ in each period.
* Resources require recurrent preventive maintenance operations since the realization of tasks diminish their remaining usage time.
* A maintenance operation takes exactly $m$ periods and cannot be interrupted. It restores the resource's remaining usage time to exactly $H$ units.

@@

* In @Cho2011, US Army aircraft were assigned daily operations over a year to aircraft in order to minimize the maximum number of maintenances.
* In @Kozanidis2008, Greek aircraft had monthly assignments of maintenances and flight hours in order to maximize the availability and final state of squadrons.
* In @Verhoeff2015, monthly assignments were done and several objectives were taken into account: availability, serviceability and final state.
* In @Chastellux2017, an initial version of the model was done, assigning missions instead of only flight hours.
* In @Seif2018, a generalization was done in order to deal with different types of maintenances and an heterogeneus fleet.

@@

* Asignments to missions are done instead of assignments of flight hours.
* Missions need to be assigned for a minimal duration.
* This model also features several improvements in the MIP modelling that permit greater instance sizes.

## Complexity analysis

Similar to the 'Fixed interval scheduling' problem.

Let $P = {1, ..., n}$ be the set of tasks to be assigned and $E = {1, ..., m}$ the set of employees. Each task $p \in P$ has a duration $u_p$ , a start time $s_p$ and a finish time $f_p$ = $s_p + u_p$ . Each employee $e$ has a set of tasks $P_e \in P$ that he/she can perform. Similarly, for each task $p$, a set $E_p \in E$ exists, which contains all employees that can perform task $p$. Both $T_e$ and $E_p$ are defined based on qualifications, time windows of tasks and availabilities of employees.

<!-- TODO: make a design. -->

@@

@@

@@

@@

* **Add more constraints**: storage of aircraft.
* **Add robustness**: duration of maintenances, new /different missions, unavailable aircraft.
